---
title: "Homework 6"
author: "Junzhe Shao"
date: "12/4/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(mgcv)
library(glmnet)
```
## Problem 1

### data cleaning


```{r}
birthw_dt <- read_csv("birthweight.csv")
#nrows(birthw_dt %>% drop_na())
birthw_dt = birthw_dt %>% mutate(babysex = factor(babysex),
                                 frace = factor(frace),
                                 malform = factor(malform),
                                 mrace = factor(mrace))
```
we find that we still have `r nrow(birthw_dt %>% drop_na())` variables after removing NA, so there is no missing value for the original data.
and convert numeric to factor where appropriate.

We try a discovery of variables using lasso.
```{r}
y = birthw_dt %>% select(bwt) %>% data.matrix()
x = birthw_dt %>% select(-bwt) %>% data.matrix()
set.seed(1)
cv_model <- cv.glmnet(x, y, alpha = 1)
#plot(cv_model)
lambda_se = cv_model$lambda.1se
best_model <- glmnet(x, y, alpha = 1, lambda = lambda_se)
c =  coef(best_model)
inds<-which(c!=0)
variables<-row.names(c)[inds][-1]
f = paste("bwt ~ ",paste(variables, collapse = " + "),sep = "")
#cat(f)
```
using the variables selected through lasso, the new formula is `r paste("bwt ~ ",paste(variables, collapse = " + "),sep = "")`
```{r}

model = lm(as.formula(f), data = birthw_dt)
model %>% broom::tidy()
res = add_residuals(birthw_dt, model)
pred = add_predictions(birthw_dt, model)

#residual and prediction data
res %>%mutate(
    pred = pull(pred,pred)
  ) %>% 
ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  labs(
    x = "Prediction",
    y = "Residuals"
  )
```

```{r}
set.seed(1)
cv_df <- crossv_mc(birthw_dt, n = 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_result <- cv_df %>% 
  mutate(
    lasso_model  = map(train, ~lm(as.formula(f), data = .x)),
    model_1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_2  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_lasso = map2_dbl(lasso_model, test, ~rmse(model = .x, data = .y)),
    rmse_model_1    = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y))
  )
cv_result %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
# Problem 2
```{r}
#load data
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
```{r}
set.seed(1)
boot_straps <- weather_df %>%
  modelr::bootstrap(n = 5000)

res_boot = boot_straps %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin , data = .x) ),
    glance = map(models, broom::glance),
    tidy= map(models, broom::tidy)
  ) %>%
  select(c(-strap,-models))

res_boot %>% unnest(glance)%>% 
  ggplot(aes(x = r.squared)) + geom_density()
coef = res_boot %>% unnest(tidy) %>% select(.id,term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% mutate(log_beta_0_beta_1 = log(`(Intercept)` * tmin))
res_boot %>% unnest(tidy) %>% select(.id,term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% mutate(log_beta_0_beta_1 = log(`(Intercept)` * tmin))%>% 
  ggplot(aes(x = log_beta_0_beta_1)) + geom_density()

```
Both of these parameters' result of bootstrapping are normally distributed.


The 95% confidence intervals for $\hat{r}^{2}$ and $\log \left(\hat{\beta}_{0} * \hat{\beta}_{1}\right)$: 
```{r}
res_boot %>% unnest(glance)%>% 
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975))


res_boot %>% unnest(tidy) %>% select(.id,term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% mutate(log_beta_0_beta_1 = log(`(Intercept)` * tmin))%>% 
  summarize(
    ci_lower = quantile(log_beta_0_beta_1, 0.025), 
    ci_upper = quantile(log_beta_0_beta_1, 0.975))
```


